---
title: "BDSM Analyses"
author: "Andy Chan"
date: "`r Sys.Date()`" 
output: 
  html_document: 
    code_folding: hide 
    theme: darkly
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(haven)
library(tidyverse) 
library(naniar) # missingness
library(car) # for Anova()
library(MVN) # Multivariate normality  
library(QuantPsyc) # Multivariate normality  
library(broom)
library(ggplot2)
library(GGally)
library(CCA)
library(CCP)

# Useful settings
options(digits = 3)
options(scipen = 9999) # suppress scientific notation

rm(list = ls()) 
dat<- readRDS("Final Cleaned Kink2.rds")
dat<-dat%>% dplyr::select(-COMMUNITY_1:-COMMUNITY_6)
# Get number of missings per variable (n and %)
miss_var_summary(dat)
dat <- dat[complete.cases(dat),] #197 cases remain
# 
# pred<-dat %>% dplyr::select(Women, Bottom, Switch, Hetero, ASSERT, YOST_Wrong_ln, YOST_V_ln, YOST_LoT, YOST_RL, YR_PRACTICE, YR_COMMUN, COMMUN)
# consent<-dat %>% dplyr::select(ASSUME, POS, PBC_ln, RLN, IBA, AWARE_ln, RCUS_ln, LIKELY_ln)

```
Not enough sample size to look at enbys, especially when we do interaction

```{r}
table(dat$Gender)
table(dat$BDSMRole)
table(dat$Gender,dat$BDSMRole)
```


Additive models

* Potential Confounders: AGE AGE_SEX PARTNERS ASSERT;  Hetero White Rel_1 Rel_2 (committed relationship as comparison group)
* Predictors:  YOST (YOST_Wrong YOST_V YOST_LoT YOST_RL) YR_PRACTICE YR_COMMUN COMMUN
* Factors:  Woman BDSM_2 BDSM_3
* Outcomes: ASSUME POS PBC_ln RLN IBA AWARE_ln RCUS_ln EFFECTIVE_ln LIKELY_ln

1. Controls: AGE AGE_SEX PARTNERS ASSERT Hetero White Rel_1 Rel_2 
2. Gender_1 Gender_3 BDSM_2 BDSM_3
3. Gender x Role Interaction
4. BDSM Attitudes: YOST (YOST_Wrong YOST_V YOST_LoT YOST_RL) 
5. BDSM Community: YR_PRACTICE YR_COMMUN COMMUN

Multivariate Outcomes: ASSUME POS PBC_ln RLN IBA AWARE_ln RCUS_ln EFFECTIVE_ln LIKELY_ln

# With Assert 
intercept-only model
```{r}
mlm1<-lm(cbind( ASSUME, POS, PBC_ln, RLN, IBA, AWARE_ln, RCUS_ln, LIKELY_ln) ~ 1, data = dat)
# summary(mlm1)
```
removed effectiveness 

add controls
```{r}
mlm2 <- update(mlm1, . ~ . + ASSERT)

anova(mlm1, mlm2)
# summary(mlm2)
```

add main demographic factors
```{r}

mlm3a <- update(mlm2, . ~ .  +Hetero)
anova(mlm2, mlm3a)
```

```{r}
mlm3b <- update(mlm3a, . ~ . + Gender+BDSMRole)
anova(mlm3a, mlm3b)
# summary(mlm3)
```

add interaction term
```{r}
mlm3c <- update(mlm3b, . ~ . + Gender*BDSMRole)
anova(mlm3b, mlm3c)
# summary(mlm3a)
```

did not significantly improve model so let's remove interaction
```{r}
mlm3d <- update(mlm3c, . ~ . -Gender*BDSMRole + Gender+BDSMRole)
anova(mlm3c, mlm3d)
```

add bdsm attitudes variables
```{r}
mlm4 <- update(mlm3d, . ~ . + YOST_Wrong_ln +YOST_V_ln +YOST_LoT +YOST_RL)
anova(mlm3d, mlm4)
# summary(mlm4)
```

add bdsm community variables
```{r}
mlm5 <- update(mlm4, . ~ . +COMMUN )
anova(mlm4, mlm5)
```
adding years practice does not improve much

```{r}
mlm6 <- update(mlm5, . ~ . +YR_COMMUN +YR_PRACTICE  )
anova(mlm5, mlm6)
```



No


# Without Assert 
intercept-only model
```{r}
mlm1<-lm(cbind( ASSUME, POS, PBC_ln, RLN, IBA, AWARE_ln, RCUS_ln, LIKELY_ln) ~ 1, data = dat)
# summary(mlm1)
```
removed effectiveness 

add main demographic factors

```{r}
mlm2 <- update(mlm1, . ~ . + Gender+BDSMRole)
anova(mlm1, mlm2)


mlm1a <- update(mlm2, . ~ . + Gender:BDSMRole)
anova(mlm2, mlm1a)

# summary(mlm3)
```
did not significantly improve model so let's remove interaction,

```{r}

mlm3 <- update(mlm2, . ~ .  +Hetero)
anova(mlm2, mlm3)
```


add bdsm attitudes variables
```{r}
mlm4 <- update(mlm3, . ~ . + YOST_Wrong_ln +YOST_V_ln +YOST_LoT +YOST_RL)
anova(mlm3, mlm4)
# summary(mlm4)

```



```{r}
mlm5a <- update(mlm4, . ~ . +YR_PRACTICE)
anova(mlm4, mlm5a)

mlm5b <- update(mlm4, . ~ . +YR_COMMUN)
anova(mlm4,mlm5b)


mlm5a <- update(mlm4, . ~ . +YR_PRACTICE+YR_COMMUN)
anova(mlm4, mlm5a)
 
```


add bdsm community variables
```{r}
mlm6 <- update(mlm5a, . ~ . +COMMUN )
anova(mlm5, mlm6)

summary(mlm6)


mlm5 <- update(mlm4, . ~ . +COMMUN )
anova(mlm4, mlm5)

summary(mlm5)
```
 
```{r}


mlm6 <- update(mlm5, . ~ . +ASSERT )
anova(mlm5, mlm6)

summary(mlm6)

```

# Go back and remove Yost

```{r}
mlm5a <- update(mlm3, . ~ . +YR_PRACTICE)
anova(mlm3, mlm5a)

mlm5b <- update(mlm3, . ~ . +YR_COMMUN)
anova(mlm3,mlm5b)


mlm5a <- update(mlm3, . ~ . +YR_PRACTICE+YR_COMMUN)
anova(mlm3, mlm5a)
 
```


add bdsm community variables
```{r}
mlm5 <- update(mlm3, . ~ . +COMMUN )
anova(mlm3, mlm5)

# summary(mlm5)
```
 
```{r}
mlm6 <- update(mlm5, . ~ . +ASSERT )
anova(mlm5, mlm6)

summary(mlm6)
```

No

# A matter of curiosity, does BDSM predict Assertiveness?
```{r}
mlm1<-lm(ASSERT ~ 1, data = dat)
mlm2 <- update(mlm1, . ~ . + Gender+BDSMRole)
anova(mlm1, mlm2)
mlm1a <- update(mlm2, . ~ . + Gender:BDSMRole)
anova(mlm2, mlm1a)

mlm3 <- update(mlm2, . ~ .  +Hetero)
anova(mlm2, mlm3)
mlm5a <- update(mlm3, . ~ . +YR_PRACTICE+YR_COMMUN)
anova(mlm3, mlm5a)
 
mlm6 <- update(mlm5a, . ~ . +COMMUN )
anova(mlm5a, mlm6)

summary(mlm6)
```
 
 
# A matter of curiosity, relationships with Yost?
```{r}
mlm1<-lm(cbind(YOST_Wrong_ln ,YOST_V_ln ,YOST_LoT ,YOST_RL) ~ 
           Gender*BDSMRole +Hetero +YR_PRACTICE+YR_COMMUN +COMMUN , data = dat)
summary(mlm1)
```

# Assertiveness as an outcome

add main demographic factors
```{r}
mlm1<-lm(cbind(ASSERT, ASSUME, POS, PBC_ln, RLN, IBA, AWARE_ln, RCUS_ln, LIKELY_ln) ~ 1, data = dat)
mlm2 <- update(mlm1, . ~ . + Gender+BDSMRole)
anova(mlm1, mlm2)

mlm1a <- update(mlm2, . ~ . + Gender:BDSMRole)
anova(mlm2, mlm1a)

# did not significantly improve model so let's remove interaction,

mlm3 <- update(mlm2, . ~ .  +Hetero)
anova(mlm2, mlm3)

mlm5a <- update(mlm3, . ~ . +YR_PRACTICE+YR_COMMUN)
anova(mlm3, mlm5a)

mlm6 <- update(mlm5a, . ~ . +COMMUN )
anova(mlm5a, mlm6)
```


```{r}
summary(mlm6)
```

## Adding Yost back in
```{r}
mlm6a <- update(mlm6, . ~ . + YOST_Wrong_ln +YOST_V_ln +YOST_LoT +YOST_RL)
anova(mlm6, mlm6a)

summary(mlm6a)
```



# Anova results exportt
```{r} 
ANOVA<-anova(mlm1,mlm2,mlm3,mlm5a,mlm6,mlm6a,mlm6b)
sink("anova.txt");print(ANOVA);sink()
results<-summary(mlm6a) 
coefs<-tidy(mlm6a)


mlm<-lm(cbind(scale(ASSERT),scale(ASSUME), scale(POS), scale(PBC_ln), scale(RLN), scale(IBA), scale(AWARE_ln), scale(RCUS_ln), scale(LIKELY_ln)) ~   Hetero + Gender + BDSMRole + scale(YOST_Wrong_ln) + scale(YOST_V_ln) + scale(YOST_LoT) + scale(YOST_RL) + scale(COMMUN) + scale(YR_PRACTICE) + scale(YR_COMMUN), data=dat)
std.coefs<-tidy(mlm)$estimate

coefs<-cbind(std.coefs=std.coefs, coefs)  %>% 
    mutate(coef=paste(round(estimate,2),"(",round(std.error,2),")",sep=""),
           sig = case_when(p.value<.001 ~ "***",
                           p.value<.01 ~ "**",
                           p.value<.05 ~ "*",
                           T~""),
           beta=paste(round(std.coefs,2),sig,sep=""))%>% 
    dplyr::select(response,term,coef,beta, estimate, std.error,std.coefs, statistic,p.value)


table<-cbind("adj.r.squared","f","numdf","dendf")
for (i in 1:9){ 
    table<-rbind(table,
                 cbind(round(results[[i]]$adj.r.squared,3), 
                       round(results[[i]]$fstatistic[1],3), 
                       round(results[[i]]$fstatistic[2],3), 
                       round(results[[i]]$fstatistic[3],3))
    )
}
colnames(table)<-table[1,]
table<-table[-1,]
table<-as.data.frame(table)
table[,1]<-as.numeric(table[,1])
table[,2]<-as.numeric(table[,2])
table[,3]<-as.numeric(table[,3])
table[,4]<-as.numeric(table[,4])
table$p <- pf(table[,2],table[,3],table[,4],lower.tail=F)

table<-table %>% 
    mutate(sig= case_when(p<.001 ~ "p<.001",T~paste("p=",round(p,3))),
            Ftest=paste("F(",numdf,", ", dendf,") = ", f, ", ",sig,sep="")
    ) %>% dplyr::select(adj.r.squared,Ftest)
            

library(openxlsx)
BDSMResults <- createWorkbook("BDSMResults") 
addWorksheet(BDSMResults, "ANOVAs")
writeData(BDSMResults, sheet = 1, ANOVA) 
addWorksheet(BDSMResults, "coefficients")
writeData(BDSMResults, sheet = 2, coefs) 
addWorksheet(BDSMResults, "modela")
writeData(BDSMResults, sheet = 3, table) 
saveWorkbook(BDSMResults, "MVR Results_242024.xlsx", overwrite = TRUE) 
 
```

```{r}
variables<-dat %>% dplyr::select(ASSERT, ASSUME, POS, PBC_ln, RLN, IBA, AWARE_ln, RCUS_ln, LIKELY_ln,
                YOST_Wrong_ln ,YOST_V_ln ,YOST_LoT ,YOST_RL, YR_PRACTICE,YR_COMMUN ,COMMUN )
    # library('apaTables')

# Use apa.cor.table function
apa.cor.table(variables)
apa.cor.table(variables, show.conf.interval = F, filename="CorTable1.doc")


apa.reg.table(mlm6a)
```


# Export no yost
```{r} 
results<-summary(mlm6) 
coefs<-tidy(mlm6)


mlm<-lm(cbind(scale(ASSERT),scale(ASSUME), scale(POS), scale(PBC_ln), scale(RLN), scale(IBA), scale(AWARE_ln), scale(RCUS_ln), scale(LIKELY_ln)) ~   Hetero + Gender + BDSMRole+ scale(COMMUN) + scale(YR_PRACTICE) + scale(YR_COMMUN), data=dat)
std.coefs<-tidy(mlm)$estimate

coefs<-cbind(std.coefs=std.coefs, coefs)  %>% 
    mutate(coef=paste(round(estimate,2),"(",round(std.error,2),")",sep=""),
           sig = case_when(p.value<.001 ~ "***",
                           p.value<.01 ~ "**",
                           p.value<.05 ~ "*",
                           T~""),
           beta=paste(round(std.coefs,2),sig,sep=""))%>% 
    dplyr::select(response,term,coef,beta, estimate, std.error,std.coefs, statistic,p.value)


table<-cbind("adj.r.squared","f","numdf","dendf")
for (i in 1:9){ 
    table<-rbind(table,
                 cbind(round(results[[i]]$adj.r.squared,3), 
                       round(results[[i]]$fstatistic[1],3), 
                       round(results[[i]]$fstatistic[2],3), 
                       round(results[[i]]$fstatistic[3],3))
    )
}
colnames(table)<-table[1,]
table<-table[-1,]
table<-as.data.frame(table)
table[,1]<-as.numeric(table[,1])
table[,2]<-as.numeric(table[,2])
table[,3]<-as.numeric(table[,3])
table[,4]<-as.numeric(table[,4])
table$p <- pf(table[,2],table[,3],table[,4],lower.tail=F)

table<-table %>% 
    mutate(sig= case_when(p<.001 ~ "p<.001",T~paste("p=",round(p,3))),
            Ftest=paste("F(",numdf,", ", dendf,") = ", f, ", ",sig,sep="")
    ) %>% dplyr::select(adj.r.squared,Ftest)
            

library(openxlsx)
BDSMResults <- createWorkbook("BDSMResults") 
addWorksheet(BDSMResults, "ANOVAs")
writeData(BDSMResults, sheet = 1, ANOVA) 
addWorksheet(BDSMResults, "coefficients")
writeData(BDSMResults, sheet = 2, coefs) 
addWorksheet(BDSMResults, "modela")
writeData(BDSMResults, sheet = 3, table) 
saveWorkbook(BDSMResults, "MVR Results_noyost_242024.xlsx", overwrite = TRUE) 
 
```



# No Years
```{r} 

mlm6b <- update(mlm6, . ~ . -YR_PRACTICE-YR_COMMUN)
anova(mlm6b)


results<-summary(mlm6b) 
coefs<-tidy(mlm6b)


mlm<-lm(cbind(scale(ASSERT),scale(ASSUME), scale(POS), scale(PBC_ln), scale(RLN), scale(IBA), scale(AWARE_ln), scale(RCUS_ln), scale(LIKELY_ln)) ~   Hetero + Gender + BDSMRole+ scale(COMMUN) , data=dat)
std.coefs<-tidy(mlm)$estimate

coefs<-cbind(std.coefs=std.coefs, coefs)  %>% 
    mutate(coef=paste(round(estimate,2),"(",round(std.error,2),")",sep=""),
           sig = case_when(p.value<.001 ~ "***",
                           p.value<.01 ~ "**",
                           p.value<.05 ~ "*",
                           T~""),
           beta=paste(round(std.coefs,2),sig,sep=""))%>% 
    dplyr::select(response,term,coef,beta, estimate, std.error,std.coefs, statistic,p.value)


table<-cbind("adj.r.squared","f","numdf","dendf")
for (i in 1:9){ 
    table<-rbind(table,
                 cbind(round(results[[i]]$adj.r.squared,3), 
                       round(results[[i]]$fstatistic[1],3), 
                       round(results[[i]]$fstatistic[2],3), 
                       round(results[[i]]$fstatistic[3],3))
    )
}
colnames(table)<-table[1,]
table<-table[-1,]
table<-as.data.frame(table)
table[,1]<-as.numeric(table[,1])
table[,2]<-as.numeric(table[,2])
table[,3]<-as.numeric(table[,3])
table[,4]<-as.numeric(table[,4])
table$p <- pf(table[,2],table[,3],table[,4],lower.tail=F)

table<-table %>% 
    mutate(sig= case_when(p<.001 ~ "p<.001",T~paste("p=",round(p,3))),
            Ftest=paste("F(",numdf,", ", dendf,") = ", f, ", ",sig,sep="")
    ) %>% dplyr::select(adj.r.squared,Ftest)
            

library(openxlsx)
BDSMResults <- createWorkbook("BDSMResults") 
addWorksheet(BDSMResults, "ANOVAs")
writeData(BDSMResults, sheet = 1, ANOVA) 
addWorksheet(BDSMResults, "coefficients")
writeData(BDSMResults, sheet = 2, coefs) 
addWorksheet(BDSMResults, "modela")
writeData(BDSMResults, sheet = 3, table) 
saveWorkbook(BDSMResults, "MVR Results_noyostnoyears_242024.xlsx", overwrite = TRUE) 
 
```

