---
title: "BDSM Analyses"
author: "Andy Chan"
date: "`r Sys.Date()`" 
output: 
  html_document: 
    code_folding: hide 
    theme: darkly
    toc: yes
    toc_depth: 5
    toc_float: yes
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(haven)
library(tidyverse) 
library(naniar) # missingness
library(car) # for Anova()
library(MVN)

# Useful settings
options(digits = 3)
options(scipen = 9999) # suppress scientific notation

rm(list = ls()) 
alldat<- readRDS("Final Cleaned Kink.rds")
alldat<-alldat %>% mutate(Woman = case_when(Gender_2==1~1,
                                            Gender_1==1~0,
                                            Gender_3==1~NA_real_))
alldat2<-alldat%>% dplyr::select(id, Gender_2,Gender_3,BDSM_2, BDSM_3, Hetero:Urban,Rel_1, Rel_2, AGE_SEX, PARTNERS, YR_PRACTICE, YR_COMMUN, COMMUNITY_1:COMMUNITY_6, ASSERT:YOST_RL, COMMUN)#, -BDSM_1, -College, -Urban, -White)
# # 296 cases, 42 variables

```

# Multivariate regressions
* Potential Confounders: AGE AGE_SEX PARTNERS ASSERT;  Hetero White Rel_1 Rel_2 (committed relationship as comparison group)
* Predictors:  YOST (YOST_Wrong YOST_V YOST_LoT YOST_RL) YR_PRACTICE YR_COMMUN COMMUN
* Factors:  Woman BDSM_2 BDSM_3
* Outcomes: ASSUME POS PBC_ln RLN IBA AWARE_ln RCUS_ln EFFECTIVE_ln LIKELY_ln

## Stepwise Regression
```{r}
update_y.formula <- function(depvar, fm) {
  as.formula(paste0(depvar, " ~ ", paste(all.vars(fm)[-1], collapse=" + ")))
}
step1 <- function(depvar, orig_fm){
  fm <- update_y.formula(depvar, orig_fm)
  step(lm(fm, data=dat))
}

depvars <- c("ASSUME", "POS", "PBC_ln", "RLN", "IBA", "AWARE_ln", "RCUS_ln", "EFFECTIVE_ln", "LIKELY_ln")
fm <- ASSUME ~ AGE_SEX  +ASSERT+ YOST_Wrong_ln +YOST_V_ln +YOST_LoT +YOST_RL+ YR_PRACTICE +YR_COMMUN+ COMMUN + Gender_2+Gender_3 + BDSM_2+ BDSM_3
res <- lapply(depvars, step1, orig_fm=fm)
```

### Stepwise Results
```{r}
lapply(res, function(x) summary(x))
knitr::kable(lapply(res, function(x) lm.beta(x)))
```

1) ASSUME: YOST_V_ln, YOST_RL, -COMMUN, -Woman, BDSM_3
2) POS: -YOST_V_ln, Commun
3) PBC_ln:  Assert, YOST_V_ln, -Yost_LoT, -Commun
4) RLN: YOST_V_ln, Yost_RL
5) IBA: -Partners, -Assert, YOST_V_ln, -Commun, BDMS_2, BDSM_3
6) AWARE_ln: -Assert, YR_Practice, Commun, Woman
7) RCUS_ln: -Age_sex, Assert, YOST_V_ln, Yost_Rl, Woman
8) EFFECTIVE_ln:  YOST_Wrong_ln, Yost_RL, -YR_Commun, -BDSM_2, -BDSM_3
9) LIKELY_ln: -Age_sex, Parners, YOST_V_ln, Yost_RL, -Commun, -BDSM_2

### Additive models
```{r}
#define intercept-only model
mlm1<-lm(cbind( ASSUME, POS, PBC_ln, RLN, IBA, AWARE_ln, RCUS_ln, EFFECTIVE_ln, LIKELY_ln) ~ 1, data = dat)
mlm2 <- update(mlm1, . ~ . + AGE_SEX+ ASSERT)
mlm3 <- update(mlm2, . ~ . + Gender_2+Gender_3+ BDSM_2+ BDSM_3 +Hetero)
mlm4 <- update(mlm3, . ~ . + YOST_Wrong_ln +YOST_V_ln +YOST_LoT +YOST_RL)
mlm5 <- update(mlm4, . ~ . + YR_PRACTICE +YR_COMMUN+ COMMUN)
anova(mlm1, mlm2,mlm3,mlm4,mlm5)
```

### Adding confounders last
```{r}
mlm1<-lm(cbind( ASSUME, POS, PBC_ln, RLN, IBA, AWARE_ln, RCUS_ln, EFFECTIVE_ln, LIKELY_ln) ~ 1, data = dat)
mlm2 <- update(mlm1, . ~ . + YOST_Wrong_ln +YOST_V_ln +YOST_LoT +YOST_RL)
mlm3 <- update(mlm2, . ~ . + YR_PRACTICE +YR_COMMUN+ COMMUN)
mlm4 <- update(mlm3, . ~ . + Gender_2+Gender_3+ BDSM_2+ BDSM_3+Hetero)
mlm5 <- update(mlm4, . ~ . + AGE_SEX + ASSERT)
anova(mlm1, mlm2,mlm3,mlm4,mlm5)
```

### Subtractive
```{r}
mlm1 <- lm(cbind( ASSUME, POS, PBC_ln, RLN, IBA, AWARE_ln, RCUS_ln, EFFECTIVE_ln, LIKELY_ln)  ~ AGE_SEX +ASSERT+
    YOST_Wrong_ln +YOST_V_ln +YOST_LoT +YOST_RL+ YR_PRACTICE +YR_COMMUN+ COMMUN +
     Gender_2+Gender_3+ BDSM_2+ BDSM_3, data=dat)

mlm2 <- update(mlm1, . ~ . - AGE_SEX - ASSERT)
mlm3 <- update(mlm2, . ~ . - Gender_2 - Gender_3- BDSM_2- BDSM_3-Hetero)
mlm4 <- update(mlm3, . ~ . - YOST_Wrong_ln -YOST_V_ln -YOST_LoT -YOST_RL- YR_PRACTICE )
anova(mlm1, mlm2,mlm3,mlm4)
```