---
title: "BDSM Analyses"
author: "Andy Chan"
date: "`r Sys.Date()`" 
output: 
  html_document: 
    code_folding: hide 
    theme: darkly
    toc: yes
    toc_depth: 5
    toc_float: yes
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(haven)
library(tidyverse) 
library(naniar) # missingness
library(car) # for Anova()
library(MVN) # Multivariate normality  
library(QuantPsyc) # Multivariate normality  

library(ggplot2)
library(GGally)
library(CCA)
library(CCP)

# Useful settings
options(digits = 3)
options(scipen = 9999) # suppress scientific notation

rm(list = ls()) 
alldat<- readRDS("Final Cleaned Kink.rds")#%>% 

dat<-alldat%>% dplyr::select(id, Women,Bottom,Switch, Gender, BDSMRole,Hetero:Urban, Single, Casual, Committed, AGE_SEX, PARTNERS, YR_PRACTICE, YR_COMMUN, ASSERT:YOST_RL, COMMUN)#, -BDSM_1, -College, -Urban, -White)
# # 296 cases, 42 variables
```
Not enough sample size to look at enbys, especially when we do interaction

# Missingness
```{r}
paste("Number of missing data points", n_miss(dat))
paste("Proportion of data missing: ", round(100*prop_miss(dat),2), "%",sep="")

# Get number of missings per participant (n and %)
miss_case_summary(dat)
miss_case_table(dat)

# Get number of missings per variable (n and %)
miss_var_summary(dat)
#
```

```{r}
dat<-dat %>% dplyr::select(-Women,-Gender)
dat <- dat[complete.cases(dat),] #218 cases remain
dat<-dat %>% dplyr::mutate(ID = row_number())

#218 cases remain
predictors<-dat %>% dplyr::select(ASSERT, YOST_Wrong, YOST_V, YOST_LoT, YOST_RL, YR_PRACTICE, YR_COMMUN, COMMUN)
outcomes<-dat %>% dplyr::select(ASSUME, POS, PBC, RLN, IBA, AWARE, RCUS, LIKELY_COERCE)
```

# Mardia's Test of Multivariate Normality
```{r} 
# Multivariate normality of Predictors
mult.norm(outcomes)$mult.test
mvn(predictors, mvnTest="mardia", univariateTest = c("SW"),desc=F) 
# Multivariate normality of Outcomes
mult.norm(outcomes)$mult.test
mvn(outcomes, mvnTest="mardia", univariateTest = c("SW"),desc=F) 
```
https://www.statology.org/multivariate-normality-test-r/
...Not normal :(

## Removing significant outliers
```{r}
# dat2<-dat %>% dplyr::select(id,Man:YR_COMMUN, ASSERT:COMMUN)

dat$pred.mahal<-mahalanobis(predictors, colMeans(predictors), cov(predictors))
dat$out.mahal<-mahalanobis(outcomes, colMeans(outcomes), cov(outcomes))

dat$pred.p <- pchisq(dat$pred.mahal, df=9, lower.tail=FALSE)
dat$out.p <- pchisq(dat$out.mahal, df=8, lower.tail=FALSE)

pred.outliers<-dat %>% filter(pred.p<.001) %>% dplyr::select(id,pred.mahal:pred.p)
out.outliers<-dat %>% filter(out.p<.001) %>% dplyr::select(id,out.mahal:out.p)

pred.outliers
out.outliers
OutlierIDs<-c(pred.outliers$id,out.outliers$id) 


dat<-alldat%>% dplyr::select(id, Women,Bottom,Switch, Gender, BDSMRole,Hetero:Urban, Single, Casual, Committed, AGE_SEX, PARTNERS, YR_PRACTICE, YR_COMMUN, COMMUNITY_1:COMMUNITY_6, ASSERT:YOST_RL, COMMUN)
df<-dat %>% filter(!id %in% OutlierIDs)
#206 cases remain
```


```{r}
pred<-df %>% dplyr::select(ASSERT, YOST_Wrong, YOST_V, YOST_LoT, YOST_RL, YR_PRACTICE, YR_COMMUN, COMMUN)
consent<-df %>% dplyr::select(ASSUME, POS, PBC, RLN, IBA, AWARE, RCUS, LIKELY_COERCE)

# Multivariate normality of Predictors
# mult.norm(pred)$mult.test
mvn(pred, mvnTest="mardia", univariateTest = c("SW"),desc=F)
# Multivariate normality of Outcomes
# mult.norm(consent)$mult.test
mvn(consent, mvnTest="mardia", univariateTest = c("SW"),desc=F)
```
https://www.statology.org/mahalanobis-distance-r/


## Transformations?
```{r}
# Predictors....
par(mfrow = c(2, 4))
par(mar=c(1,1,1,1))
hist(df$ASSERT)
hist(df$YOST_Wrong)
hist(df$YOST_V)
hist(df$YOST_LoT)
hist(df$YOST_RL)
hist(df$YR_PRACTICE)
hist(df$YR_COMMUN)
hist(df$COMMUN)
```


```{r}
par(mfrow = c(2, 4))
par(mar=c(1,1,1,1))
hist(df$ASSUME)
hist(df$POS)
hist(df$PBC)
hist(df$RLN)
hist(df$IBA)
hist(df$AWARE)
# hist(df$RCUS) 
hist(df$LIKELY_COERCE) 
```
based on the shape of distributions above, ln transform...Yost_wrong, Yost_V, PBC, Aware, RCUS, EFFECTIVE and LIKELY_COERCE

```{r, fig.width=8, fig.height=8}
dat<-df
dat<-dat %>% dplyr::mutate(YOST_Wrong_ln = log(YOST_Wrong), 
                   YOST_V_ln = log(YOST_V), 
                   PBC_ln = log(PBC), 
                   AWARE_ln = log(AWARE), 
                   RCUS_ln = log(RCUS),
                   # EFFECTIVE_ln = log(EFFECTIVE_COERCE), 
                   LIKELY_ln = log(LIKELY_COERCE))

par(mfrow = c(2, 3))
par(mar=c(1,1,1,1))
hist(dat$YOST_Wrong_ln)
hist(dat$YOST_V_ln)
hist(dat$PBC_ln)
hist(dat$AWARE_ln)
hist(dat$RCUS_ln)
# hist(dat$EFFECTIVE_ln)
hist(dat$LIKELY_ln)

pred<-dat %>% dplyr::select(ASSERT, YOST_Wrong_ln, YOST_V_ln, YOST_LoT, YOST_RL, YR_PRACTICE, YR_COMMUN, COMMUN)
consent<-dat %>% dplyr::select(ASSUME, POS, PBC_ln, RLN, IBA, AWARE_ln, RCUS_ln,LIKELY_ln)


mvn(pred, mvnTest="mardia", univariateTest = c("SW"),desc=F) 
mvn(consent, mvnTest="mardia", univariateTest = c("SW"),desc=F) 
```
Still no multivariate normality...!!!! 
Note: Removed RCUS and Effective

```{r}
saveRDS(dat, "Final Cleaned Kink2.rds")
```